---
title: "analysis with all derived formaulas and using package"
author: "Mehwish Zaman"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
  
  
  
  Generate data from biveriate package to see the likelihood function vales is near to true value also the estimates 
```{r}
partrue<- c(3.2, 3.5,0.47,0.55, 0.45)## True parameter value
d<- c(1,2)
s1<- partrue[2]/(d[1]^(partrue[4])) ### s(d)= s_o * d^(-eta)
s2<- partrue[2]/(d[2]^(partrue[4]))
u1 <- partrue[1]*s1                    ### u(d)= tilda(u)*s(d)
u2 <- partrue[1]*s2
k1 <- partrue[3]
k2<- partrue[3]
mr1 <- c(u1,s1,k1)
mr2<- c(u2,s2,k2)
data_new<-evd::rbvevd(500, dep = partrue[5], model = "log", mar1 = mr1, mar2 = mr2)
colnames(data_new)<- c("d1","d2")
data_new
```
  
  
  
  
  
independent dgev model for all duration here for the demo we take only two columns with d=1 2
```{r}
x1<-data_new[,1]
x2<-data_new[,2]
annualmax <- data.frame(x1,x2)
likehood<-function(par,d,annualmax) {
  ### IDF-parameters :IDF model for d[1,72]:
  mu<-par[1]
  sigma<-par[2]
  gamma<-par[3]
  eta<-par[4]
  d<-c(1,2)
  epsi<-10^(-16)
  lh.mat<-array(0,dim=dim(annualmax))
  Y<-array(0,dim=dim(annualmax))
  ### Loop over rainfall durations #####
  for (i in 1:length(d)) {
    sigma_d<-sigma*(d[i])^(-eta) 
    mu_d<- mu*sigma_d
    Y[,i]<-1+gamma*(annualmax[,i]-mu_d)/sigma_d
    if(any(eta <= epsi || eta > 1-epsi)) return(10^6)
    if (min(Y[,i],na.rm=TRUE)>0) {
      lh.mat[,i]<- -log(sigma_d)-Y[,i]^(-1/gamma)-(1+1/gamma)*log(Y[,i])   ### GEV-loglikelihood for duration d[i]
    } 
    else {
      lh.mat[,i]<--10^10
    }
  }
  ##################################
  ### Make sum of the log-likelihoods over the years and rainfall durations d, and return
  
  return(-sum(lh.mat,na.rm=TRUE))
}
likehood(par = par0, d=d, annualmax=ff)
par0<-c(2.080, 1.170, 0.630, 0.070 ) ## Inital Value for Optimisation 
result_r<-optim(par0,likehood,annualmax=ff, method = "Nelder-Mead", hessian = T, control=list(maxit=5000)) 
result_r
```
  


Bivariate logistic model from coles 2001

```{r}

x1<-data_new[,1]
x2<-data_new[,2]
data1 <- data.frame(x1,x2)

Bivnlik <- function(par, data1, debug=FALSE)###negative loglike for bivariate logistic model 
{
  epsi<- 10^(-6)
  mu<-par[1]
  sigma_o<- par[2]
  k<- par[3]
  eta<- par[4]
  a <- par[5]
  if (debug) cat(mu,sigma_o,k,eta,a," ")
  d <- c(1,2)
  s1 <- (sigma_o)/(d[1])^eta
  s2 <- (sigma_o)/(d[2])^eta
  m1 <- mu * s1
  m2 <- mu * s2
  y1<- (pmax(0, (1 + (k * (data1$x1 - m1)/s1))))^(1/k)
  y2<- ( pmax(0, (1 + (k * (data1$x2 - m2)/s2))))^(1/k)
  y <- (1/(y1^(1/a))+1/(y2^(1/a)))
  if(any(y1<= 0)||any(y2 <= 0 ) || any(s1 <= 0) || any(s2 <= 0)|| any(y <= 0)) return(10^6)
  if(eta <= epsi || eta >= 1-epsi)return(10^6)
   if(any(a <= epsi ) || any(a > 1-epsi)) return(10^6)
  g<- -sum(-log(s1)-log(s2)-(y)^a + (a - 2)*log(y) + log(y^a - 1+ 1/a)- (1/a)*log(y1)-k*log(y1)- (1/a)*log(y2)-k*log(y2), na.rm = TRUE)
  if (debug) cat(g,"\n")
  return(g)
}
Bivnlik(par=partrue, data1=data1, debug=TRUE)
optim2 <- optim(par=partrue, Bivnlik, data1=data1, debug=TRUE, method = "Nelder-Mead", hessian = T, control=list(maxit=5000))
optim2


```

#Markove dgev model for likelihood 


```{r   mc_nllh}
x1<-data_new[,1]
x2<-data_new[,2]
mcdata <- data.frame(x1,x2)

mc_nllh <- function(mc_par,d, mc_data, debug=FALSE)
{
  epsi<- 10^(-6)
  mu<-mc_par[1]
  sigma_o<- mc_par[2]
  k<- mc_par[3]
  eta<- mc_par[4]
  a <- mc_par[5]
  if (debug) cat(mu,sigma_o,k,eta,a," ")
  s1 <- (sigma_o)/(d[1])^eta
  s2 <- (sigma_o)/(d[2])^eta
  m1 <- mu * s1
  m2 <- mu * s2
  y1<- (pmax(0, (1 + (k * (mc_data[,1] - m1)/s1))))^(1/k)
  y2<- ( pmax(0, (1 + (k * (mc_data[,2] - m2)/s2))))^(1/k)
  y <- (1/(y1^(1/a))+1/(y2^(1/a)))
  if(any(y1<= 0)||any(y2 <= 0 ) || any(s1 <= 0) || any(s2 <= 0)|| any(y <= 0)) return(10^6)
  if(eta <= epsi || eta >= 1-epsi)return(10^6)
   if(any(a <= epsi ) || any(a > 1-epsi)) return(10^6)
  g<- -sum(-log(s1)-log(s2)-(y)^a + (a - 2)*log(y) + log(y^a - 1+ 1/a)- (1/a)*log(y1)-k*log(y1)- (1/a)*log(y2)-k*log(y2)-log(s1)- 1/y1- (1+k)*log(y1), na.rm = TRUE)
  if (debug) cat(g,"\n")
  return(g)
} 
d <- c(1,2)
mc_nllh(mc_par=partrue, d=d, mc_data=mcdata, debug=TRUE)
optim2 <- optim(partrue, mc_nllh,d=d, mc_data=mcdata, debug=TRUE, method = "Nelder-Mead", hessian = T, control=list(maxit=5000))
optim2




```





#####using dbvevd package  for bivariate 
```{r}
dgev.dbvevd<- function(x,d,mu,sigma_o,k,eta,dep){
  epsi<- 10^(-6)
  if(eta <= epsi || eta >= 1-epsi)return(10^6)
  s1 <- (sigma_o)/(d[1])^eta
  s2 <- (sigma_o)/(d[2])^eta
  m1 <- mu * s1
  m2 <- mu * s2
  return(evd::dbvevd(x,dep=dep, mar1 = c(m1,s1,k), mar2 = c(m2,s2,k), log = TRUE ))
  
  
}
d<-c(1,2)
sum(dgev.dbvevd(x=mcdata,d=d,mu=3.2,sigma_o=3.5,k=0.47,eta=0.55,dep=0.45))

```

#Markove dgev for two durations 
```{r}
dgev.dbvevd<- function(x,d,mu,sigma_o,k,eta,dep){
  epsi<- 10^(-6)
  if(eta <= epsi || eta >= 1-epsi)return(10^6)
  s1 <- (sigma_o)/(d[1])^eta
  s2 <- (sigma_o)/(d[2])^eta
  m1 <- mu * s1
  m2 <- mu * s2
  return(evd::dbvevd(x,dep=dep, mar1 = c(m1,s1,k), mar2 = c(m2,s2,k), log = TRUE )-evd::dgev(x[,1],m1,s1,k))
  
}
d<-c(1,2)
sum(dgev.dbvevd(mcdata,d=d,mu=3.2,sigma_o=3.5,k=0.47,eta=0.55,dep=0.45))

```


```{r}
########## conditional duration dependence likelihood function for gev model
cdd.gev<- function(x,pr,d){
  epsi<- 10^(-6)
  mu<-pr[1]
  sigma<- pr[2]
  xi<- pr[3]
  eta<- pr[4]
  dep <- pr[5]
  epsi<- 10^(-6)
  if(eta <= epsi || eta >= 1-epsi)return(10^6)
  if(dep <= epsi || dep >= 1-epsi)return(10^6)
  ##### calculates the negative log-likelihood of the first 
  ###column of data(x, matrix of data with more than two columns) using the generalized extreme value distribution with parameters mu, sigma, and k, here d=1.
  nllik<- -sum(evd::dgev(x[,1], loc = mu, scale = sigma, shape = xi, log = TRUE)) 
  for (i in 2:(ncol(x))) {###loop over the durations form d=2 to M=ncol(x)
    s1 <-sigma*(d[i])^(-eta)
    s2 <-sigma*(d[i-1])^(-eta) 
    m1 <- mu*s1
    m2 <- mu*s2
    nllik<- nllik-sum(evd::dbvevd(x[,c(i-1,i)],dep=dep, mar2 = c(m1, s1,xi), mar1 = c(m2,s2,xi), log = TRUE )-evd::dgev(x[,i-1], loc = m2, scale = s2,shape = xi, log=TRUE))
  
  }
  return(nllik)
  
}
d<-  1:72
ff<- st1_maxh[,-1] ### data with multiple columns 
partrue<- c(1.76, 1.48, 0.48,0.04, 0.05)
cdd.gev(x=ff,d=d, partrue)
op <- optim( x=ff,fn = cdd.gev,partrue, d=d, method = "Nelder-Mead", hessian = T, control=list(maxit=5000))
op

```
###pairwise bivariate 





```{r}
d<- 1:24
xdata<- Bocholt.h_maxh[,-1]
partrue<- c(1.76,1.48,0.48,0.037,0.065)
output <- matrix(NA, nrow = length(d)-1, ncol = length(partrue))
# Define the function for the pair
  dbvevd_pair <- function(mpar, d, data) {
    epsi<- 10^(-6)
    mu<-mpar[1]
    sigma<- mpar[2]
    xi<- mpar[3]
    eta<- mpar[4]
    a <- mpar[5]
    if(eta <= epsi || eta >= 1-epsi)return(10^6)
    if(a <= epsi || a >= 1-epsi)return(10^6)
    #if (debug) cat(mu,sigma,xi,eta,a," ")
    s1 <- (sigma)/(d[1])^eta
    s2 <- (sigma)/(d[2])^eta
    m1 <- mu * s1
    m2 <- mu * s2
    return(-sum(dbvevd(data,dep=a,model = "log", mar1 = c(m1,s1,xi),mar2 = c(m2,s2,xi), log = TRUE),na.rm=TRUE ))
  }
  for (i in 1:(length(d)-1)) {
    # Apply optimization for the pair
  optimc_pair <- optim(partrue, dbvevd_pair,d=d[i:(i+1)], data=xdata[,i:(i+1)], method = "Nelder-Mead", hessian = T, control=list(maxit=5000))
  
  # Save the output in the matrix
  output[i,] <- optimc_pair$par

}
  
output
# Print the output matrix
colnames(output)<- c("mu","sigma","xi","eta","a")
output
par(mfrow = c(1, 3))
plot(output[,5], xlab="durations", ylab="alpha")
abline(h = 0.023, col = "red")

plot(output[,1], xlab="durations", ylab="mu")
abline(h = 0.03, col = "blue")

plot(output[,3], xlab="durations", ylab="xi")
abline(h = 0.7, col = "green")



```







```{r Asymptotic Independence}
output1<- 1-output[,5]
taildep_results <- list()

# Number of columns in the dataset
num_cols <- ncol(runmean)

# Perform taildep calculations using a for loop
for (i in 1:(num_cols - 1)) {
  # Calculate taildep for each pair of columns (i, i+1)
  taildep_result <- taildep(runmean[, i], runmean[, i + 1], u = 0.90, type = "chi")
  
  # Name the result based on the column indices
  taildep_name <- paste0("chi", i, i + 1)
  
  # Add the result to the taildep_results list
  taildep_results[[taildep_name]] <- taildep_result
}
#tail<- as.matrix(taildep_results)
taildep_results
unlist(taildep_results)
emptaildep<- c(0.6886745,   0.7992152 ,  0.8352418,   0.8519903,   0.8657994,   0.8849406,   0.8953316   ,0.9065429, 0.9065429,   0.9046971,   0.8904096 ,  0.9020310  , 0.9236333,   0.9106446,   0.9205570,   0.9193949,0.9103028 ,  0.9034666 ,  0.9253423,   0.9324519 ,  0.9314949,   0.9339559,   0.9361434   )
plot(output1, type = "b", xlab = "durations at lag 1", ylab = "tail dependent Coefficient", xlim = c(1, 25), ylim = c(0.6, 1), col = "black", pch = 16)
lines(emptaildep, type = "b", col = "red", pch = 16)
abline(h = 0.977, col = "blue")
legend("bottomright", legend = c("Bivariate duration depdendent logistic parameter", "Asymptotic Independence, chi at u=0.90", "Conditional duration dependent logistic parameter "),
       col = c("black", "red", "blue"), lty = c(1, 1, 1), pch = c(16, 16, NA),
       bty = "n")

```


```{r}
q1<- quantile(sort(runmean[,1]), 0.90)
q11<- runmean[,1]>q1
q2<- quantile(sort(runmean[,2]), 0.90)
q21<- runmean[,2]>q2
g<- taildep(q11, q21, u=0.90)
```
```{r}
1-0.023
```

